Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2014-02-04 paper/main.tex
first dump section 1

\section{Theoretical Precedents}
\label{sec:theory}

... There is abundant literature on the issue of shape and angular momentum
aligmnent of dark matter haloe with respect to the cosmic web.

... This alignment is often measured from the distribution of the
$\cos\theta$ where $\theta$ is the angle between the two axes of
interest.

... Table 1 and Table 2 summarizes recent results found in the literature for
shape and angular momentum alignment. The Appendix includes a detailed
description of each one the algorithms.

The main summary from these results can be done in three points. (i)
The halo mass of $1-5\times 10^{12}$\hMsun is a threshold mass between
different behaviours.  (ii) Halo shape is strongly aligned along
filaments, more so for massive haloes and (iii) Halo spin tends to be
perpendicular with respect to filaments, but it is a weak.

@@

\begin{equation}
P(\cos\theta) =
(1-c)\sqrt{1+\frac{c}{2}}\left[1-c\left(1-\frac{3}{2}\cos^{2}\theta
  \right)\right]^{-3/2}, 
\end{equation}

>>>>

\section{Theoretical Considerations: Notation and Precendents}
\label{sec:theory}

There is abundant literature on the issue of shape and angular momentum
aligmnent of dark matter haloe with respect to the cosmic web. In this
paper we focus our attention on results published during the last
decade that have made use of large N-body dark matter only
cosmological simulations. There are many works that have addressed
this problem using observational data from large surveys such as the
Sloan Digital Sky Survey (SDSS), however we choose to narrow our
discussion to simulation based studies which are prone to comparison.

Out of the three alignments that we study in this paper -shape,
angular momentum and peculiar velocity- only the the first two have
received wide attention in the literature, being angular momentum the
most popular with twice the number of studies for shape alignment.

These alignments are often measured from the distribution of the
$\mu=\vert\cos\theta\vert$ where $\theta$ is the angle between the two axes of
interest. This is often directly measuered as the absolute value of
the dot product between the two unit vectors along the directions
being tested, for instance in the case of angular momentum one would compute
$\mu=\vert\hat{j}\cdot\hat{n}\vert$ In the case of shape alignments the major
axis is the chosen direction to compare against the cosmic web.

For an isotropic ditribution of the vector around the direction defined by
$\hat{n}$ the $\mu$ distribution, ranging between $0$ and $1$, should
be flat and its mean value shoud be
$\langle|mu|\rangle=0.5$. If a distribution is biased towards $1$
($\langle\vert\mu\vert\rangle>0.5$) we call this an statistical
alignment along $\hat{n}$, while in the case of a bias towards $0$
($\langle\vert\mu\vert\rangle<0.5$) we talk about an anti-alignment,
meaning an perpendicular orientations with respecto to the $\hat{n}$
direction.

\cite{Trowland2013} presented a parameterization for the $\mu$
distribution in the case of angular momentm alignment based on
theoretical considerations by \cite{Lee2005} (Eq. \ref{eq:distro} in
the Appendix A). Under this parameterization it was found a unique
correspondece between the full shape of the $\vert\mu\vert$
distribution and its average. In this paper we use that result to only
present the results for the average $\langle\vert\mu\vert\rangle$.

Table 1 and Table 2 summarize recent results found in the literature for
shape and angular momentum alignment. The Appendix A includes a detailed
description of the definitions, algorithms and simulations used in
each one of these studies. In these tables the first column describe
the reference, the second column summarizes the web finding method
with a single name, the third scale associates an spatial scale to the
web finding methods, in most cases it corresponds to the grid size or
smoothing scale used to interpolate the underlying matter density or
velocity field; The fourth column indicates along which web element
(filament or wall) was measured the alignment; the fifth scale
indicates the strenght of the alignment/anti-alignment, $++$/$--$
indicate a strong alignement/anti-alignment while $+$/$-$ indicate a
weaker signal; the last columns indicates whether the described signal
is only present in a defined range of halo mass.

These results can be summarized in three important points:
\begin{itemize}
\item The halo mass of $1-5\times 10^{12}$\hMsun is a threshold mass between
behaviours of no-alignment, alignment or anti-alignment.
\item Halo shape provides a strong alignment signal along filaments
  and sheets, more so for massive haloes. 
\item Halo spin tends to be oriented perpendicular to filaments and
parallel to sheets, but it is a weaker than shape alignment. 
\end{itemize}

@@

\begin{equation}
P(\cos\theta) =
(1-c)\sqrt{1+\frac{c}{2}}\left[1-c\left(1-\frac{3}{2}\cos^{2}\theta
  \right)\right]^{-3/2}, 
\label{eq:distro}
\end{equation}
